Rapid cycleway prioritisation tool

### 2020-05-29 code/index.Rmd
Update intro

The aim of this tool is to help reveal the locations that have the best potential for pop-up cycleways. It should be used together with local knowledge, to prioritise where to install rapid measures to support safe travel as part of the COVID-19 response. We anticipate that this may be used in the development of a range of temporary, experimental and longer term measures to make the streets safer for us all, as new travel patterns and behaviours emerge in the coming weeks and months.

@@

We have focused on roads which are sufficiently wide that part of the roadspace could potentially be reallocated to pop-up cycleways without preventing traffic movement. In identifying these locations, we have not taken average traffic volumes into account. The pandemic has had a severe impact on movement and traffic flows are currently below normal levels. Instead, we simply identify streets that have multiple vehicle lanes or a carriageway width of greater than 10m.

@@

We have used several types of data. The cycling potential of each road is estimated according the Propensity to Cycle Tool's Government Target scenario, which represents the government target to double cycling levels by 2025. Our figures include both travel to work and travel to school, and are based on 2011 Census data. Data on road widths and number of lanes is derived from the Cycling Infrastructure Prioritisation Toolkit.

@@

>>>>

The aim of this tool is to help reveal the locations that have the greatest potential for new cycleways. It should be used together with local knowledge, to prioritise where to install rapid measures to support safe travel as part of the COVID-19 response. We anticipate that this may be used in the development of a range of temporary, experimental and longer term measures to make the streets safer for us all, as new travel patterns and behaviours emerge in the coming weeks and months.

@@

We have focused on roads which are sufficiently wide that part of the road space could potentially be reallocated to provide additional space for active transport without preventing traffic movement. In identifying these locations, we have not taken average traffic volumes into account. The pandemic has had a severe impact on movement and traffic flows are currently below normal levels. Instead, we simply identify streets that have multiple vehicle lanes or a carriageway width of greater than 10m.

@@

The cycling potential of each road is based on data from the Propensity to Cycle Tool (see [www.pct.bike](https://www.pct.bike/) for further details) and represents the number of one way cycle trips to work and school that could be expected when the [Government's aim of doubling cycling is met](https://www.gov.uk/government/publications/cycling-and-walking-investment-strategy).
The scenario assumes cycling grows evenly nationwide accounting for distance and hilliness.
Our figures include data on travel to work from 2011 Census data and travel to school. Data on road widths and number of lanes is derived from the Cycling Infrastructure Prioritisation Toolkit.

@@

# Known issues and limitations

Road names ...
